\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-10 experience.tex
Some additions regarding Fabric model.

\emph{Azure Service Faric} (or \emph{Fabric} for short) is a platform and API for creating reliable services that execute on a cluster of machines. The developer writes a service that receives requests (e.g.\ from some client program via HTTP) and mutates its state based on these requests. In order to make the service \emph{reliable}, Fabric launches several copies (\emph{replicas}) of the service, where each copy runs as a separate process on different nodes in the cluster. One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary. Fabric exposes several different APIs that developers can use to write services.

>>>>

\emph{Azure Service Faric} (or \emph{Fabric} for short) is a platform and API for creating reliable services that execute on a cluster of machines. The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. In order to make the service \emph{reliable}, Fabric launches several copies (\emph{replicas}) of the service, where each copy runs as a separate process on a different node in the cluster. One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries by sending \emph{replication requests} so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary.

Fabric services have a lot of asynchrony, which make them interesting targets for systematic testing with \psharp{}.
Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The system that we wished to test is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
Prior work~\cite{deligiannis2015psharp}
created a model of Fabric with limited functionality;
it used a mixture of \csharp{} and \psharp{} internally,
only supported one in-flight replication request
(which restricts the asynchrony that can be tested),
and only supported one Fabric service.
Our new Fabric model was re-written to use only \psharp{}
internally,
support an arbitrary number of Fabric services and in-flight replication requests,
and in general be a more complete model of Fabric.
Note that \csharp{} code is still required to interface with the existing
\csharp{} service code.
We refer to our \csharp{} code
as the \emph{translation layer}
and
 the user-written \csharp{} service code as \emph{user code}.

\begin{figure}[thb]
\centering
\includegraphics[width=\linewidth, clip=true, trim=0 180px 440px 0]{img/FabricModelOverview}
\caption{Overview of the key machines (rounded boxes) and interfaces (boxes) in our Fabric model.}
\label{fig:fabric_model}
\end{figure}

An overview of our Fabric model is shown in Figure~\ref{fig:fabric_model}.
The \texttt{ClusterRuntime} machine 
handles the creation and management of 
one or more Fabric services,
as well as service resolution requests
which allows for client-service and inter-service communication
within the model.
Each Fabric service instance is managed by a \texttt{ServiceRuntime}
machine, which in turn manages 
several \texttt{ReplicaRuntime} machines.
Each \texttt{ReplicaRuntime} communicates with the user code
via several machines and interfaces from the translation layer
(only the translation layer for the primary is shown,
but every \texttt{ReplicaRuntime} has its own instance of the translation layer).
Note that communication between machines is hierachical;
thus, communication between \texttt{ReplicaRuntime}s
(such as the sending of replication requests)
is via the \texttt{ServiceRuntime} machine for that service.
This approach does not necessarily reflect how Fabric works in practice.
Instead, we chose an architecture
that keeps the model simple
while still allowing (what we believe to be) realistic
asynchrony and failure scenarios.
